Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2023-08-16 2_SSL_NE/article/article_main.tex
some more edits

Our LED manufacturing cost model shows a 95.5\% decrease in the cost of producing low-to-mid power GaN-based white classic-chip LEDs from 1.11$ to 0.05$ (in 2020 USD) between 2003 and 2020. In contrast with LED performance improvements, where progress was driven mostly by innovations in LED technology, the dramatic decline in LED manufacturing cost has been a product of higher yields across manufacturing steps and economies of scale resulting from increases in the sapphire wafer size , with the former factor contributing to XX\% and latter factor contributing to YY\% of the overall LED cost reduction over time . Both were enabled by advances in manufacturing equipment (e.g., for epitaxy and chip dicing) and incremental manufacturing process improvements from learning-by-doing.  Surprisingly, LED innovations and associated technology spillovers are not found to have a substantial impact on LED manufacturing cost reductions over time. [PLACEHOLDER TO DISCUSS THE REASONS FOR THAT].

>>>>

Our LED manufacturing cost model shows a 95.5\% decrease in the cost of producing low-to-mid power GaN-based white classic-chip LEDs from 1.11\$ to 0.05\$ (in 2020 USD) between 2003 and 2020. In contrast with LED performance improvements, where progress was driven mostly by innovations in LED technology, the dramatic decline in LED manufacturing cost has been a product of higher yields across manufacturing steps and economies of scale resulting from increases in the sapphire wafer size. Both were enabled by advances in manufacturing equipment (e.g., for epitaxy and chip dicing) and incremental manufacturing process improvements from learning-by-doing. Surprisingly, LED innovations and associated technology spillovers are not found to have a substantial impact on LED manufacturing cost reductions over time. [PLACEHOLDER TO DISCUSS THE REASONS FOR THAT].
